Unified Linear Speedup Analyses of Communication-Efficient Stochastic FedAvg and Nesterov FedAvg

### 2021-07-18 source/sec_intro.tex
Update on Overleaf.

\textbf{Other Related Works} Since the proposal of the original FedAvg algorithm, an active area of research in Federated Learning has focused on designing new algorithms that address the various challenges in FL, such as dealing with diverging data distributions \cite{sattler2020clustered}, improving communication efficiency \cite{chen2019communication,xu2020ternary,zhu2019multi}, reducing communication cost via compression or sparsification \cite{alistarh2017qsgd,wangni2017gradient,jiang2019improving,li2020acceleration}, and accelerating stochastic optimization methods with variance reduction \cite{horvath2019stochastic,dinh2020federated} Nevertheless, FedAvg remains a practically popular algorithm whose linear speedup behavior is desirable. In the distributed optimization setting, there have been a line of works \cite{liu2016collective,yuan2016convergence,yuan2020stochastic,yuan2018optimal} that deal with constrained optimization problems, often under convexity assumptions. Convergence results, especially with linear speedup analyses, in constrained Federated Learning settings are relatively less common \cite{wang2019adaptive}, and remains an open research area that deserves more attention.

>>>>

\textbf{Other Related Works} Since the proposal of the original FedAvg algorithm, an active area of research in Federated Learning has focused on designing new algorithms that address the various challenges in FL, such as dealing with diverging data distributions \cite{sattler2020clustered}, improving communication efficiency \cite{sattler2019robust,chen2019communication,xu2020ternary,zhu2019multi,zhou2021communication}, reducing communication cost via compression or sparsification \cite{alistarh2017qsgd,wangni2017gradient,jiang2019improving,li2020acceleration}, and accelerating stochastic optimization methods with variance reduction \cite{horvath2019stochastic,dinh2020federated} Nevertheless, FedAvg remains a practically popular algorithm whose linear speedup behavior is desirable. In the distributed optimization setting, there have been a line of works \cite{liu2016collective,yuan2016convergence,yuan2020stochastic,yuan2018optimal} that deal with constrained optimization problems, often under convexity assumptions. Convergence results, especially with linear speedup analyses, in constrained Federated Learning settings are relatively less common \cite{wang2019adaptive}, and remains an open research area that deserves more attention.
